### 2014-04-10 cs250-hw/hw1.tex
c1

Now, note that both $V\Sigma^+U^Ty$ and $(X^TX)^{-1}X^T$ satisfy the requirements for being the Moore-Penrose pseudoinverse of $X$, so they must be equal. Thus, we have $\h{\beta}=(X^TX)^{-1}X^Ty$.
\ssn{b}
$HX=X(X^TX)^{-1}X^TX=X$
\ssn{c}
$H^T=(X(X^TX)^{-1}X^T)^T=X(X^TX)^{-T}X^T=X(X^TX)^{-1}X^T$
\ssn{d}
$HH=X(X^TX)^{-1}X^TX(X^TX)^{-1}X^T=X(X^TX)^{-1}X^T=H$
\ssn{e}
By (d), $H$ is a projection matrix. Thus, we just need to show that the image of $H$ is the column space. Since the image of $X$ is the column space (a subset of $\rn^n$), this means that we need to show that $(X^TX)^{-1}X^T$ has rank $d$ (or that its image is all of $\rn^d$). This is true because $(X^TX)^{-1}$ is invertible and $X^T$ has rank $d$ also. 
\ssn{f}
Traces of products are invariant under cyclic permutation, so $\tr(H)=\tr(X(X^TX)^{-1}X^T)=\tr(X^TX(X^TX)^{-1})=\tr(I_d)=d$.
\subsection*{3}
\ssn{b}
I have a general policy against running unknown scripts on my computer, and since I know that I have a large part of the Python toolchain set up already, I decided to read the setup script (\verb|toolkit.sh|) and replicate the necessary parts.

>>>>

Now, note that both $V\Sigma^+U^TX$ and $(X^TX)^{-1}X^T$ satisfy the requirements for being the Moore-Penrose pseudoinverse of $X$. The calculations are a bit tedious to type out and not very illuminating, so I'll omit them. Thus, by the uniqueness of the pseudoinverse, they must be equal. Thus, we have $\h{\beta}=(X^TX)^{-1}X^Ty$.
\ssn{b}
$HX=X(X^TX)^{-1}X^TX=X$
\ssn{c}
$H^T=(X(X^TX)^{-1}X^T)^T=X(X^TX)^{-T}X^T=X(X^TX)^{-1}X^T$
\ssn{d}
$HH=X(X^TX)^{-1}X^TX(X^TX)^{-1}X^T=X(X^TX)^{-1}X^T=H$
\ssn{e}
By (d), $H$ is a projection matrix. Thus, we just need to show that the image of $H$ is the column space. Since the image of $X$ is the column space (a subset of $\rn^n$), this means that we need to show that $(X^TX)^{-1}X^T$ has rank $d$ (or that its image is all of $\rn^d$). This is true because $(X^TX)^{-1}$ is invertible and $X^T$ has rank $d$ also. 
\ssn{f}
Traces of products are invariant under cyclic permutation, so $\tr(H)=\tr(X(X^TX)^{-1}X^T)=\tr(X^TX(X^TX)^{-1})=\tr(I_d)=d$.
\subsection*{3}
\ssn{b}
I have a general policy against running unknown scripts on my computer, and since I know that I have a large part of the Python toolchain set up already, I decided to read the setup script (\verb|toolkit.sh|) and replicate the necessary parts.
